---
title: "Assignment 3 - Part 2 - Diagnosing Schizophrenia from Voice"
author: "Riccardo Fusaroli"
date: "October 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3 - Diagnosing schizophrenia from voice

In the previous part of the assignment you generated a bunch of "features", that is, of quantitative descriptors of voice in schizophrenia, focusing on pitch.
In the course of this assignment we will use them to try to automatically diagnose schizophrenia from voice only, that is, relying on the set of features you produced last time, we will try to produce an automated classifier.

### Question 1: Can you diagnose schizophrenia from pitch range only? If so, how well?

Build a logistic regression to see whether you can diagnose schizophrenia from pitch range only.

Calculate the different performance measures (accuracy, sensitivity, specificity, PPV, NPV, ROC curve) on a logistic regression using the full dataset. Don't forget the random effects!

Then cross-validate the logistic regression and re-calculate performance on the testing folds. N.B. The cross-validation functions you already have should be tweaked: you need to calculate these new performance measures.

N.B. the predict() function generates log odds (the full scale between minus and plus infinity). Log odds > 0 indicates a choice of 1, below a choice of 0.
N.B. you need to decide whether calculate performance on each single test fold or save all the prediction for test folds in one datase, so to calculate overall performance.
N.B. Now you have two levels of structure: subject and study. Should this impact your cross-validation?



```{r}
##### PREPARATION
library(caret)
library(lme4)
library(lmerTest)
library(pROC)

#Read file
d = read.csv("Pitch_Out_Data.csv")

#Make into factors
d$Subject = as.factor(d$Subject)
d$Study = as.factor(d$Study)

#Create ID as numbers for use in folding
d$fold_id = as.numeric(d$Subject)

#Scale continous variables to make convering easier
d$P_Mean = scale(d$P_Mean)
d$P_SD = scale(d$P_SD)
d$P_Range = scale(d$P_Range)
d$P_Median = scale(d$P_Median)
d$P_IQR = scale(d$P_IQR)
d$P_MeanAbDif = scale(d$P_MeanAbDif)
d$P_CovofVar = scale(d$P_CovofVar)
d$P_RR = scale(d$P_RR)
d$P_DET = scale(d$P_DET)
d$P_NRLINE = scale(d$P_NRLINE)
d$P_maxL = scale(d$P_maxL)
d$P_L = scale(d$P_L)
d$P_ENTR = scale(d$P_ENTR)
d$P_LAM = scale(d$P_LAM)
d$P_TT = scale(d$P_TT)

```

```{r}

##### BUILD MODEL
 
#Create model. TUrning off time consuming derivative calculation - makes the model less accurate, but can converge. Do not include subject, because it's 50 - 50 - it shouldn't have effect on the outcome. Study should be included if: there's a different amount of schizo etc in different studies. There might be.
model1 = glmer(Diagnosis ~ P_Range + (1 |Study), d, family = "binomial")
summary(model1)

##### Get confuson matrix scores

#Create predictions for model
d$PredictionsPerc=predict(model1)

#Define what is control and what is schizo
d$Predictions[d$PredictionsPerc>0]="Control"
d$Predictions[d$PredictionsPerc<=0]="Schizophrenia"
#Create a confusion matrix
ScoreMatrix = confusionMatrix(data = d$Predictions, reference = d$Diagnosis, positive = "Schizophrenia") 
###Extract scores
ScoreMatrix$overall[1]
ScoreMatrix$byClass

#Create a ROC Curve
rocCurve <- roc(response = d$Diagnosis,   predictor = d$PredictionsPerc)
plot(rocCurve, legacy.axes = TRUE) 
#Find area under curve
auc(rocCurve)
#Find confidence intervals
ci (rocCurve)

```

```{r}

###### MAKE A LOOP TO CROSS VALIDATE RESULTS

#Create list of the models to test
Ms = c("Diagnosis ~ P_Mean + (1 |Study)", 
       "Diagnosis ~ P_SD + (1 |Study)",
       "Diagnosis ~ P_Range + (1 |Study)",
       "Diagnosis ~ P_Median + (1 |Study)",
       "Diagnosis ~ P_IQR + (1 |Study)",
       "Diagnosis ~ P_MeanAbDif + (1 |Study)",
       "Diagnosis ~ P_CovofVar + (1 |Study)",
       "Diagnosis ~ P_RR + (1 |Study)",
       "Diagnosis ~ P_DET + (1 |Study)",
       "Diagnosis ~ P_NRLINE + (1 |Study)",
       "Diagnosis ~ P_maxL + (1 |Study)",
       "Diagnosis ~ P_L + (1 |Study)",
       "Diagnosis ~ P_ENTR + (1 |Study)",
       "Diagnosis ~ P_LAM + (1 |Study)",
       "Diagnosis ~ P_Range + P_MeanAbDif + P_CovofVar + (1 |Study)",
       "Diagnosis ~ P_L + P_LAM + P_TT + (1 |Study)",
       "Diagnosis ~ P_CovofVar + P_LAM + P_TT + (1 |Study)",
       "Diagnosis ~ P_LAM + P_TT + (1 |Study)",
       "Diagnosis ~ P_Range + P_MeanAbDif + P_CovofVar + P_L + P_LAM + P_TT + (1 |Study)",
       "Diagnosis ~ P_Range + P_SD + P_Mean + P_Median + P_IQR + P_MeanAbDif + P_CovofVar + P_RR + P_DET + P_NRLINE + P_maxL + P_L + P_ENTR + P_LAM + P_TT + (1 |Study)"
       )

#Create lists for results
SCORES = as.data.frame(NULL)

#Run Loop for all models
for (M in Ms) {
  
#Create folds
Folds = createFolds(unique(d$fold_id), 5)


#Preperations for loop - result lists and n reset
AUCl = NULL
CIl = NULL
Accl = NULL
Sensitivityl = NULL
Specificityl = NULL
PPVl = NULL
NPVl = NULL

n=1

for (i in Folds) {
  #Make a test dataset with one fold
  dtest_temp = subset(d, fold_id %in% i)
  
  #Make a training dataset with all other folds
  dtrain_temp = subset(d, !fold_id %in% i)
  
  #Make a model on the training dataset
  model_temp = glmer(M, dtrain_temp, family = "binomial")
  
  ####Create confusion matrix
  #Create predictions for model
  dtest_temp$PredictionsPerc=predict(model_temp, dtest_temp, allow.new.levels=T)
  #Define what is control and what is schizo  
  dtest_temp$Predictions[dtest_temp$PredictionsPerc>0]="Control"
  dtest_temp$Predictions[dtest_temp$PredictionsPerc<=0]="Schizophrenia"
  #Create a confusion matrix
  ScoreMatrix = confusionMatrix(data = dtest_temp$Predictions, reference = dtest_temp$Diagnosis, positive = "Schizophrenia") 
  
  #Get data from confusion matric
  Accl [n] = ScoreMatrix$overall[1]
  Sensitivityl[n] = ScoreMatrix$byClass[1]
  Specificityl [n] = ScoreMatrix$byClass[2]
  PPVl [n] = ScoreMatrix$byClass[3]
  NPVl [n] = ScoreMatrix$byClass[4]

  ####Create a ROC Curve
  rocCurve <- roc(response = dtest_temp$Diagnosis,   predictor = dtest_temp$PredictionsPerc)
    #plot(rocCurve, legacy.axes = TRUE) 
  #Find area under curve
  AUCl[n] = auc(rocCurve)
  #Find confidence intervals
  CIl[n] = ci(rocCurve)
  
    #Loop end and n+1
  n=n+1
  }

#Create row with results from model
NewRow = data.frame(Model = M, AUC = mean(AUCl), AUC_SD = sd(AUCl), CI = mean(CIl), Acc = mean(Accl), Sens = mean(Sensitivityl), Spec = mean(Specificityl), PPV = mean(PPVl), NPV = mean(NPVl))

#Add to final dataframe with all models
SCORES = rbind(SCORES, NewRow)
}



```



### Question 2 - Which single acoustic predictor is the best predictor of diagnosis?

### Question 3 - Which combination of acoustic predictors is best for diagnosing schizophrenia?

Now it's time to go wild! Use all (voice-related) variables and interactions you can think of. Compare models and select the best performing model you can find.

Remember:
- Out-of-sample error crucial to build the best model!
- After choosing the model, send Celine and Riccardo the code of your model

### Question 4: Properly report the results

METHODS SECTION: how did you analyse the data? That is, how did you extract the data, designed the models and compared their performance?

RESULTS SECTION: can you diagnose schizophrenia based on voice? which features are used? Comment on the difference between the different performance measures.

### Bonus question 5

You have some additional bonus data involving speech rate, pauses, etc. Include them in your analysis. Do they improve classification?

### Bonus question 6

Logistic regression is only one of many classification algorithms. Try using others and compare performance. Some examples: Discriminant Function, Random Forest, Support Vector Machine, etc. The package caret provides them.
